---
title: "RISE combined Aims 1 & 2"
author: "Mike Frank"
date: "2024-12-03"
output: html_document
---


```{r setup, include=T}
knitr::opts_chunk$set(echo = T, warning = F, message =  F)

# load in required packages
library(tidyverse)
library(here)
library(janitor)
library(lme4)
library(emmeans)
```


# Read in data

Please refer to the data files we have uploaded on Github under folder "Data_Aim2" and change the directory as appropriate.
Note: read.csv creates an extra column named X for row number, thus we're excluding it using [,-1].
Recode Age to be a factor variable with Age 6 as the reference group.


```{r}
tasks <- c("geosocial", "vpc", "audiovisual", "prediction", 
           "word_comprehension", "numeracy", "helperhinderer")

d_raw <- map_df(tasks, function(x) {
  a1 <- read_csv(here("Data_Aim1",paste0(x,".csv")), show_col_types = FALSE) |> mutate(version = "aim1")
  a2 <- read_csv(here("Data_Aim2",paste0(x,".csv")), show_col_types = FALSE) |> mutate(version = "aim2")
  d <- bind_rows(a1,a2) |>
    mutate(task = x)
}) |>
  janitor::clean_names() |>
  select(-x1) 
```

Outcomes:

* Geosocial: Outcome is % frames looking at social stimulus (person_good).
* VPC: Outcome is % frames looking at novel stimulus (novel_good).
* AV: Outcome is % frames looking at synchronous stimulus (synch_good).
* Prediction: Outcome is proportion of trials with an AEM (aem_prop). 
* Word Comprehension: Outcome is % target - % distracter (diff). 
* Numeracy: Outcome is % frames looking at changing stimulus (change_good).
* Helper/Hinderer: Outcome is % frames looking at helping stimulus (helper_good).


```{r}
d <- d_raw |>
  mutate(measure = case_when(task == "geosocial" ~ person_good, 
                             task == "vpc" & version == "aim1" ~ novel_good, 
                             task == "vpc" & version == "aim2" ~ novel_good_avg, 
                             task == "audiovisual" ~ synch_good, 
                             task == "prediction" ~ aem_prop,
                             task == "word_comprehension" ~ diff + .5,
                             task == "numeracy" ~ change_good,
                             task == "helperhinderer" ~ helper_good), 
         sub_id = response_uuid) |>
  select(version, sub_id, age, task, trial, usable_frames_percent, measure, stimulus_type, block) |>
  mutate(age = as_factor(age), 
         task = fct_relevel(task, tasks))

d_sub <- d |>
  group_by(version, sub_id, age, task) |>
  summarise(measure = mean(measure, na.rm = TRUE)) |>
  filter(!is.nan(measure))
```

Plot. 


```{r}
ggplot(d_sub, aes(x = age, y = measure, col = version)) + 
  geom_point(alpha = .2, position = position_dodge(width = .4)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .4), 
               pch = 2) + 
  geom_hline(yintercept = .5, lty = 2) + 
  facet_wrap(~task) + 
  ylim(0, 1) + 
  xlab("Proportion looking") +
  ggthemes::theme_few()
```
# Stats

vpc, av, and prediction have interactions (stimulus_type, stimulus_type, block)

## Geosocial 

```{r}
geo_mod <- lmer(measure ~ age * version + (1 | sub_id), filter(d, task == "geosocial"))
summary(geo_mod)
```

```{r}
emmeans(geo_mod, ~age * version)
```

## VPC

The stimulus type variable is missing for the Aim 2 VPC. 

```{r}
vpc_mod <- lmer(measure ~ age * stimulus_type * version + (1 | sub_id),
                filter(d, task == "vpc"))
summary(vpc_mod)
```

```{r}
emmeans(vpc_mod, ~age * version * stimulus_type)
```
## Audiovisual

The stimulus type variable is missing for the Aim 2 Audivisual 

```{r}
av_mod <- lmer(measure ~ age * stimulus_type * version + (1 | sub_id),
                filter(d, task == "audiovisual"))
summary(av_mod)
```

```{r}
emmeans(av_mod, ~age * version * stimulus_type)
```


## Prediction

Let's first look across blocks and then within. 

```{r}
prediction_mod <- lmer(measure ~ age * version + (1 | sub_id),
                filter(d, task == "prediction"))
summary(prediction_mod)
```

```{r}
emmeans(prediction_mod, ~age * version)
```




```{r}
prediction_block_mod <- lmer(measure ~ age * block * version + (1 | sub_id),
                filter(d, task == "prediction"))
summary(prediction_block_mod)
```

```{r}
emmeans(prediction_mod, ~age * version * block)
```


## Word comprehension 

```{r}
word_mod <- lmer(measure ~ age * version + (1 | sub_id), filter(d, task == "word_comprehension"))
summary(word_mod)
```

```{r}
emmeans(word_mod, ~age *version)
```

## Numeracy

Also a stimulus type interaction.

```{r}
numeracy_mod <- lmer(measure ~ age * version + (1 | sub_id), 
                     filter(d, task == "numeracy"))
summary(numeracy_mod)
```

```{r}
emmeans(numeracy_mod, ~ age * version)
```

```{r}
numeracy_mod_stim <- lmer(measure ~ age * stimulus_type * version + (1 | sub_id), 
                     filter(d, task == "numeracy"))
summary(numeracy_mod_stim)
```

```{r}
emmeans(numeracy_mod, ~ age * stimulus_type * version)
```
## Helper hinderer


```{r}
helperhinderer_mod <- lmer(measure ~ age * version + (1 | sub_id), filter(d, task == "helperhinderer"))
summary(helperhinderer_mod)
```

```{r}
emmeans(helperhinderer_mod, ~age * version)
```